StreamReduce: Processing Data Streams\\and Avoiding Work

### 2012-05-07 paper/paper.tex
Dynamic knobs related work

StreamReduce builds of previous work in the areas of MapReduce and Data Stream Management Systems.

@@

>>>>

StreamReduce builds of previous work in the areas of MapReduce, Data Stream Management Systems,
and approximation algorithms.

@@

\subsection{Approximation Algorithms}
An alternative to load shedding to cope with high stream throughput is to perform approximate
computations on stream data.

Dynamic Knobs~\cite{Hoffmann:2011:DKR:1950365.1950390} describes a mechanism to explore the
accuracy-performance tradeoff space to adjust dynamically adjust program tuning parameters
to changes in the execution environment. This allows programs to do things such as
utilize more resources if they become available, use less power if power rates spike,
or use less accurate computations in the face of an impending time constraint.

The most important piece Dyanmic Knobs offers to the DSMS space is dynamic
\emph{peak load provisioning}. Their system can adjust downward the amount of resources,
machines, etc. required for normal load and quickly adjust these levels back up to
handle load spikes. Combined with Aurora's load shedding, peak load provisioning can
be used to create a DSMS that uses less resources in both the normal and peak load
states.
